Turbulence in compact to giant HII regions

### 2021-06-25 mnras_template.tex
Fix package incompatibility in older latex versions
This caused an error on the overleaf site but was not a problem for me
locally

See https://tex.stackexchange.com/questions/564490/command-bbbk-already-defined-ol-bbbk-mathordamsb7c-when-i-try-t
Really fix the amssymb compatibility this time I hope
I made a mistake in the previous fix
Add hard line breaks throughout.
This is just to make diffs work better

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}

@@

Figure \ref{fig:SF604} shows similarity in our results and previous studies from \citet{tanco1997} and \citet{2019arXiv191203543M} for TAURUS-II data. \citep{2019arXiv191203543M} report $\sigma$ of 7.2 km/s while we have 7.3 km/s. Despite the agreement in observations analysis and interpretations are different. As mentioned by \citet{2019arXiv191203543M} some problems and inconsistencies arise in the results of \citet{tanco1997}; they don't consider a lower limit based on the observational seeing and that lead them to conclude about a double regime acting on the velocity spectrum. None of the previous studies present a power-law index to compare our results, but  Fig. \ref{fig:SF604} shows that the difference lies on the structure function or lag value and no on the form of the plot. With this assumption we can establish the same index of 1.7 for NGC 604 TAURUS-II observations.

>>>>

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\let\Bbbk\relax
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{multicol}

@@

Figure \ref{fig:SF604} shows similarity in our results and previous studies from \citet{tanco1997} and \citet{2019arXiv191203543M} for TAURUS-II data.
\citep{2019arXiv191203543M} report $\sigma$ of 7.2 km/s while we have 7.3 km/s.
Despite the agreement in observations analysis and interpretations are different.
As mentioned by \citet{2019arXiv191203543M} some problems and inconsistencies arise in the results of \citet{tanco1997}; they don't consider a lower limit based on the observational seeing and that lead them to conclude about a double regime acting on the velocity spectrum.
None of the previous studies present a power-law index to compare our results, but Fig.~\ref{fig:SF604} shows that the difference lies on the structure function or lag value and no on the form of the plot.
With this assumption we can establish the same index of 1.7 for NGC 604 TAURUS-II observations.
